Topological Equivariant Artist Model

### 2021-03-08 slides/main.tex
up to Q

\usepackage{amsmath,amsfonts,amssymb,pxfonts,eulervm,xspace}
\usepackage{mathrsfs} % math script fonts
\usepackage{tikz-cd} % commutative diagrams
\usepackage{subcaption} % subfigure float captioning

\usepackage{tabularx}
\usepackage{multirow}
\usepackage{graphicx}

@@

\begin{frame}{Data Bundle}
    \begin{figure}
        \includegraphics[width=1\textwidth]{figures/math/fiberbundle.png}
    \end{figure}
    a fiber bundle is a tuple $(\dtotal,\,\dbase,\,\pi ,\,\dfiber)$ defined by the projection map $\pi$
    \begin{equation}
        \label{eq:fiber_bundle}
        \begin{tikzcd}[ampersand replacement=\&]
            \dfiber \arrow[r, hook] \& \dtotal \arrow[r, "\pi"] \& \dbase
        \end{tikzcd}
    \end{equation}
\end{frame}

\begin{frame}{Variables: Fiber}
    \begin{equation}
        \dfiber = \ftotal_{\fsection(\fname)} = \ftotal_{\ftype} 
    \end{equation}
    where $\ftotal_{\fsection(\fname)}$ is 
    \begin{equation}
        \label{eq:data_types}
        \begin{tikzcd}[ampersand replacement=\&]
            \fttype \arrow[r] \arrow[d, "\pi_{\fsection}"'] \& \ftotal \arrow[d, "\pi"] \\
            \fnames \arrow[r, "\fsection"']                  \& \ftypes       
        \end{tikzcd}
    \end{equation}
    \begin{description}
        \item[\ftypes] data types of the variables in the dataset 
        \item[\ftotal] disjoint union of all values of type $\ftype \in \ftypes$ 
        \item[\fnames] variable names
        \item[\fttype] \ftotal\ restricted to the data type of a named variable   
    \end{description}
\end{frame}

\begin{frame}{Sample Fiber}
    \begin{figure}[H]
        \begin{subfigure}{.4\textwidth}
            \includegraphics[width=\textwidth]{figures/math/temp_1k.png}
            \caption{}
            \label{fig:fiber_example_plane}
        \end{subfigure}
        \begin{subfigure}{.4\textwidth}
            \includegraphics[width=\textwidth]{figures/math/temp_3f.png}
            \caption{}
            \label{fig:fiber_example_cube}
        \end{subfigure}
        \caption{}
        \label{fig:data_fiber_example}
    \end{figure}
    \begin{description}
        \item[\ref{fig:fiber_example_plane}]  $\dfiber=\reals\times\reals$, for example (time, temperature)
        \item[\ref{fig:fiber_example_cube}]  $\reals\times\realsp\times\reals$, for example  (time, wind=(speed, direction))
    \end{description}
\end{frame}

\begin{frame}{Structure of Components: Monoids}
A monoid \monoid\ is a set with
\begin{description}
    \item[associative binary operator] $\ast:\monoid \times \monoid\rightarrow \monoid$
    \item[identity element] $e\in \monoid$ such that $e\ast a= a \ast e = a$ for all $a \in \monoid$. 
\end{description}
\end{frame}
\begin{frame}{Monoid Actions}
A left monoid action of $\monoid_i$ is a set $\dfiber_i$ with an action $\bullet: \monoid\times \dfiber_i \rightarrow \dfiber_i$ with the properties:
    \begin{align*}
        \textbf{associativity}\;& \text{for all } f,g \in \monoid_i \text{ and } x\in \dfiber_i,\, f\bullet(g\bullet x) = (f\ast g) \bullet x\\
        \textbf{identity}\;& \text{for all } x\in \dfiber_i, e\in \monoid_i,\,  e\bullet x = x 
    \end{align*}
\end{frame}

\begin{frame}{Monoid Composition: Permutation}
    \begin{figure}
        \includegraphics[width=1\linewidth]{figures/math/monoid_emoji.png}
    \end{figure}
\end{frame}

\begin{frame}{Monoid Composition: Partial Order}
    \begin{figure}
        \begin{overprint}
            \onslide<1|handout:0>\includegraphics[width=1\linewidth]{figures/math/monoid_hasse.png}
            \onslide<2|handout:0>\includegraphics[width=1\linewidth]{figures/math/monoid_monotone.png}
            \onslide<3>\includegraphics[width=1\linewidth]{figures/math/monoid_maps.png}
        \end{overprint}
    \caption{Inspired by definition 1.59 diagram in Spivak and Fong's An Invitation to Applied Category Theory \cite{fongInvitationAppliedCategory2019}}
    \end{figure}
\end{frame}

\begin{frame}{Continuity: base space}
    \begin{figure}[H]
    \includegraphics[width=\linewidth]{figures/math/k_qspace.png}
    \caption{}
    \label{fig:base_space_div}
\end{figure}
where the total space can be decomposed into components 
\begin{equation}
    \pi:\dtotal_1\oplus\ldots\oplus \dtotal_i \oplus\ldots \oplus \dtotal_n \rightarrow \dbase
\end{equation}
\end{frame}

\begin{frame}{Sample: Base Space}
    \begin{figure}[H]
        \begin{subfigure}{.4\textwidth}
            \includegraphics[width=\textwidth]{figures/math/temp_1k.png}
            \label{fig:base_example_discrete}
        \end{subfigure}
        \begin{subfigure}{.4\textwidth}
            \includegraphics[width=\textwidth]{figures/math/temp_2f.png}
            \label{fig:base_example_continuous}
        \end{subfigure}
        \label{fig:base_example}
    \end{figure}
\end{frame}

\begin{frame}{Values: Section}
    For any fiber bundle, there exists a map
    \begin{equation}
        \begin{tikzcd}[ampersand replacement=\&]
            \dfiber \arrow[r, hook] \& \dtotal \arrow[d, "\pi"'] \\
                              \& \dbase \arrow[u, "\dsection"', bend right]
        \end{tikzcd}
    \end{equation}
     such that $\pi(\dsection(\dbasepoint)) = \dbasepoint$.

     The set of all global sections is denoted as $\Gamma(\dtotal)$.
\end{frame}

\begin{frame}{Record}
    Assuming a trivial fiber bundle $\dtotal = \dbase \times \dfiber$, the section is 
\begin{equation}
    \label{eq:section_return}
    \dsection(\dbasepoint) = (\dbasepoint, (g_{\dfiber_{0}}(\dbasepoint), \ldots, g_{\dfiber_{n}}(\dbasepoint)))
\end{equation}
where $g: \dbase \rightarrow \dfiber$ is the index function into the fiber.
\end{frame}

\begin{frame}{Sample dataset}
    \begin{figure}[H]
        \includegraphics[width=1\linewidth]{figures/math/fiberbundle.png}
        \label{fig:data_sections}
    \end{figure}
\end{frame}

\subsection{Graphics}
\begin{frame}{Graphic Bundle}
    The graphics bundle is a tuple $(\gtotal,\,\gbase,\,\pi ,\,\gfiber)$ defined by the projection map $\pi$
    \begin{equation}
        \label{eq:fiber_bundle}
        \begin{tikzcd}[ampersand replacement=\&]
            \gfiber \arrow[r, hook] \& \gtotal \arrow[r, "\pi"] \& \gbase
        \end{tikzcd}
    \end{equation}
\end{frame}
\begin{frame}{Continuity: Base space}
    The surjective map $\vindex: \gbase \rightarrow \dbase$ 
    \begin{equation}
        \begin{tikzcd}[ampersand replacement=\&]
            \dtotal \arrow[d, "\pi"'] \& \gtotal \arrow[d, "\pi"'] \\
            \dbase                   \& \gbase \arrow[l, "\vindex"']
        \end{tikzcd}
    \end{equation}
    goes from region $\gbasepoint \in \gbase_{\dbasepoint}$ to its associated point $\gbasepoint$. 
\end{frame}

\begin{frame}{Sample Display Target: Fiber}
    Assume a 2D opaque image $\gfiber=\reals^5$ with elements 
    \begin{equation}
    (x,\, y,\, r,\, g,\, b) \in \gfiber
    \end{equation}
    such that a rendered graphic only has 2D position and color.
\end{frame}

\begin{frame}{Continuity Retraction Maps}   
    \begin{figure}[H]
        \includegraphics[width=1\textwidth]{figures/math/retraction_maps.png}
        \label{fig:graphic_retraction_map}
    \end{figure}
\end{frame}

\begin{frame}{Rendering: Define a Pixel}
    \begin{columns}
        \column{0.5\textwidth}
        Given a pixel
        \begin{equation}
        p=\left[y_{top}, y_{bottom}, x_{right}, x_{left}\right]
        \end{equation}
        the inverse map of the bounding box 
        \begin{equation}
        \gbase_{p} ={\gsection_{xy}}^{-1}(p)
        \end{equation}
        is a region $\gbase_p \subset \gbase$ such that 
        \begin{align}
            \scriptstyle r_p &= \scriptstyle \iint\limits_{S_p} \rho_r(s)ds^{2}\\
            \scriptstyle g_p &= \scriptstyle \iint\limits_{S_p} \rho_g(s)ds^{2}\\
            \scriptstyle  b_p &= \scriptstyle \iint\limits_{S_p} \rho_b(s)ds^{2}
        \end{align}
        yields the color of the pixel. 
        \column{0.5\textwidth}
        \begin{figure}[H]
            \includegraphics[width=\textwidth]{figures/math/render.png}
        \end{figure}
    \end{columns}
\end{frame}

\subsection{Artist}

\section{References}
%\begin{frame}[allowframebreaks]{References}
%\printbibliography
%\end{frame}

>>>>

\usepackage{amsmath,amsfonts,amssymb,pxfonts,eulervm,xspace}
\usepackage{mathrsfs} % math script fonts
\usepackage{tikz}
\usetikzlibrary{calc} %boxes
\newcommand{\tikzmark}[1]{\tikz[overlay,remember picture] \node (#1) {};}
\usetikzlibrary{cd} % commutative diagrams
\usepackage{subcaption} % subfigure float captioning

\usepackage{tabularx}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{appendixnumberbeamer}

@@

\begin{frame}{Data Bundle}
    \begin{figure}
        \includegraphics[width=1\textwidth]{figures/math/fiberbundle.png}
    \end{figure}
    A fiber bundle is a tuple $(\dtotal,\,\dbase,\,\pi ,\,\dfiber)$ defined by the projection map $\pi$
    \begin{equation}
        \label{eq:fiber_bundle}
        \begin{tikzcd}[ampersand replacement=\&]
            \dfiber \arrow[r, hook] \& \dtotal \arrow[r, "\pi"] \& \dbase
        \end{tikzcd}
    \end{equation}
    where \dtotal\ is the total data space, \dfiber\ is the variable space, and \dbase\ encodes the continuity.
\end{frame}

\begin{frame}{Variables: Fiber}
    Given a space of all possible values \ftotal\
    \begin{equation}
        \label{eq:data_types}
        \begin{tikzcd}[ampersand replacement=\&]
            \fttype \arrow[r] \arrow[d, "\pi_{\fsection}"'] \& \ftotal \arrow[d, "\pi"] \\
            \fnames \arrow[r, "\fsection"']                  \& \ftypes       
        \end{tikzcd}
    \end{equation}
    a fiber component is the restricted space $\ftotal_{\fsection(\fname)}$. 
    \begin{equation}
        \dfiber = \ftotal_{\fsection(\fname)} = \ftotal_{\ftype} 
    \end{equation}
    \begin{description}
        \item[\ftypes] data types of the variables in the dataset 
        \item[\ftotal] disjoint union of all values of type $\ftype \in \ftypes$ 
        \item[\fnames] variable names, $\fname \in \fnames$
        \item[\fttype] \ftotal\ restricted to the data type of a named variable   
    \end{description}
\end{frame}

\begin{frame}{Variable types are dimensions of the fiber}
    \begin{figure}[H]
        \begin{subfigure}{.49\textwidth}
            \includegraphics[width=\textwidth]{figures/math/temp_1k.png}
            \caption{}
            \label{fig:fiber_example_plane}
        \end{subfigure}
        \begin{subfigure}{.49\textwidth}
            \includegraphics[width=\textwidth]{figures/math/temp_3f.png}
            \caption{}
            \label{fig:fiber_example_cube}
        \end{subfigure}
        \caption{}
        \label{fig:data_fiber_example}
    \end{figure}
    \begin{description}
        \item[\ref{fig:fiber_example_plane}]  $\dfiber=\reals\times\reals$, (time, temperature)
        \item[\ref{fig:fiber_example_cube}]  $\reals\times\realsp\times\reals$, (time, wind=(speed, direction))
    \end{description}
\end{frame}

\begin{frame}{Structure of Components: Monoid \& Monoid Actions}
A monoid \monoid\ is a set with
\begin{description}
    \item[associative binary operator] $\ast:\monoid \times \monoid\rightarrow \monoid$
    \item[identity element] $e\in \monoid$ such that $e\ast a= a \ast e = a$ for all $a \in \monoid$. 
\end{description}
\pause
\begin{block}{left monoid action}
A set \dfiber\ with an action $\bullet: \monoid\times \dfiber \rightarrow \dfiber$ with the properties:
    \begin{align*}
        \textbf{associativity}\;& \text{for all } f,g \in \monoid \text{ and } x\in \dfiber,\, f\bullet(g\bullet x) = (f\ast g) \bullet x\\
        \textbf{identity}\;& \text{for all } x\in \dfiber, e\in \monoid,\,  e\bullet x = x 
    \end{align*}
\end{block}
\end{frame}

\begin{frame}{Monoid Actions: Permutation}
    \begin{figure}
        \includegraphics[width=1\linewidth]{figures/math/monoid_emoji.png}
    \end{figure}
\end{frame}

\begin{frame}{Why monoids? partial orders}
    \begin{figure}
        \begin{overprint}
            \onslide<1|handout:0>\includegraphics[width=1\linewidth]{figures/math/monoid_hasse.png}
            \onslide<2|handout:0>\includegraphics[width=1\linewidth]{figures/math/monoid_monotone.png}
            \onslide<3>\includegraphics[width=1\linewidth]{figures/math/monoid_maps.png}
        \end{overprint}
    \caption{Inspired by definition 1.59 diagram in Spivak and Fong's An Invitation to Applied Category Theory \cite{fongInvitationAppliedCategory2019}}
    \end{figure}
\end{frame}

\begin{frame}{Data Continuity: Base space}
    \begin{figure}[H]
    \includegraphics[height=.5\textheight]{figures/math/k_qspace.png}
    \label{fig:base_space_div}
\end{figure}
where the total space can be decomposed into components 
\begin{equation}
    \pi:\dtotal_1\oplus\ldots\oplus \dtotal_i \oplus\ldots \oplus \dtotal_n \rightarrow \dbase
\end{equation}
\end{frame}

\begin{frame}{Data connectivity is encoded as the base space}
    \begin{figure}[H]
        \begin{subfigure}{.49\textwidth}
            \includegraphics[width=\textwidth]{figures/math/temp_1k.png}
            \caption{}
            \label{fig:base_example_discrete}
        \end{subfigure}
        \begin{subfigure}{.49\textwidth}
            \includegraphics[width=\textwidth]{figures/math/temp_2f.png}
            \caption{}
            \label{fig:base_example_continuous}
        \end{subfigure}
        \caption{}
        \label{fig:base_example}
    \end{figure}
    \begin{description}
        \item[\ref{fig:base_example_discrete}] data is discrete 0D points
        \item[\ref{fig:base_example_continuous}]  data is lies on the 1D continuous interval \dbase\
    \end{description}
\end{frame}

\begin{frame}{Values: Section}
    For any fiber bundle, there exists a map
    \begin{equation}
        \begin{tikzcd}[ampersand replacement=\&]
            \dfiber \arrow[r, hook] \& \dtotal \arrow[d, "\pi"'] \\
                              \& \dbase \arrow[u, "\dsection"', bend right]
        \end{tikzcd}
    \end{equation}
     s.t. $\pi(\dsection(\dbasepoint)) = \dbasepoint$.  Set of all global sections is denoted $\Gamma(\dtotal)$.
     \pause
     \begin{block}{Record}
     Assuming a trivial fiber bundle $\dtotal = \dbase \times \dfiber$, the section is 
\begin{equation}
    \label{eq:section_return}
    \dsection(\dbasepoint) = (\dbasepoint, (g_{\dfiber_{0}}(\dbasepoint), \ldots, g_{\dfiber_{n}}(\dbasepoint)))
\end{equation}
where $g: \dbase \rightarrow \dfiber$ is the index function into the fiber.
\end{block}
\end{frame}

\begin{frame}{Sample dataset}
    \begin{figure}[H]
        \includegraphics[width=1\linewidth]{figures/math/fiberbundle.png}
        \label{fig:data_sections}
    \end{figure}
    \begin{itemize}
        \item \dfiber\ is $\reals\times\reals$
        \item \dbase\ is interval $\left[0,1\right]$
        \item $\dsection^{(1)}$ is a $sin$ function
        \item $\dsection^{(2)}$ is a $cos$ function
        \item $\dsection^{(1)}, \dsection^{(2)} \in \Gamma(\dtotal)$
    \end{itemize}

\end{frame}

\subsection{Graphics}
\begin{frame}{Graphic Bundle}
    The graphics bundle is a tuple $(\gtotal,\,\gbase,\,\pi ,\,\gfiber)$ defined by the projection map $\pi$
    \begin{equation}
        \begin{tikzcd}[ampersand replacement=\&]
            \gfiber \arrow[r, hook] \& \gtotal \arrow[d, "\pi"'] \\
                              \& \gbase \arrow[u, "\gsection"', bend right]
        \end{tikzcd}
    \end{equation}
    where \gsection\ is the fully encoded graphic. 
    \pause
    \begin{block}{Example: 2D opaque image}
    The target display is $\gfiber=\reals^5$ with elements 
    \begin{equation*}
    (x,\, y,\, r,\, g,\, b) \in \gfiber
    \end{equation*}
    returned by \gsection\ such that a graphic has color and 2D position.
    \end{block}

\end{frame}
\begin{frame}{Graphic Continuity}
    The surjective map $\vindex: \gbase \rightarrow \dbase$
    \begin{equation}
        \begin{tikzcd}[ampersand replacement=\&]
            \dtotal \arrow[d, "\pi"'] \& \gtotal \arrow[d, "\pi"'] \\
            \dbase                   \& \gbase \arrow[l, "\vindex"']
        \end{tikzcd}
    \end{equation}
    goes from region $\gbasepoint \in \gbase_{\dbasepoint}$ to its associated point $\dbasepoint$ in data space. 
\pause
    \begin{figure}[H]
        \includegraphics[width=1\textwidth]{figures/math/retraction_maps.png}
        \label{fig:graphic_retraction_map}
    \end{figure}
\end{frame}

\subsection{Artist}
\begin{frame}{Topological Equivariant Artist Model}
The topological artist \vartist\ is a monoid equivariant sheaf map 
\begin{equation}
    \label{eq:artist_diagram}
    \begin{tikzcd}[ampersand replacement=\&]
        \dtotal^{\prime} \arrow[r, "\vchannel"] \arrow[rd, "\pi"'] \& \vtotal \arrow[d, "\pi"] \& \vindex^*\vtotal \arrow[r, "\vmark"] \arrow[d, "\vindex^*\pi"'] \arrow[l, "\vindex^*"'] \& \gtotal \arrow[ld, "\pi"] \\
                                              \& \dbase                  \& \gbase \arrow[l, "\vindex"']                                              \&                    
        \end{tikzcd}
\end{equation}

where the artist $\vartist: \mathcal{O}(\dtotal) \rightarrow \mathcal{O}(\gtotal)$ takes as input $\dtotal^{\prime}=\mathcal{J}^{2}(\dtotal)$. 
\end{frame}

\begin{frame}{Visual Bundle}
    The visual bundle is a tuple $(\vtotal,\,\dbase,\,\pi ,\,\vfiber)$ defined by the projection map $\pi$
    \begin{equation}
        \begin{tikzcd}[ampersand replacement=\&]
            \vfiber \arrow[r, hook] \& \vtotal \arrow[d, "\pi"'] \\
                              \& \dbase \arrow[u, "\vsection"', bend right]
        \end{tikzcd}
    \end{equation}
    where \vsection\ is the visual variable encoding\cite{bertinIIPropertiesGraphic2011} of the representation of the data section \dsection. 
    \begin{block}{Example: position and color}
        Given an artist with parameters $\{xpos, ypos, color\}$, a sample visual section \vsection\ could be $\{.5, .5, (255, 20,147)\}$
    \end{block}
\end{frame}

\begin{frame}{Visual Channel Encoders}
We define the visual transformers \vchannel\ on components of the data bundle $\dsection_{i}$
\begin{equation}
    \label{eq:nu_expanded}
    \{\vchannel_{0}, \ldots, \vchannel_{n}\}: \{\dsection_{0}, \ldots, \dsection_{n}\} \mapsto \{\vsection_{0}, \ldots, \vsection_{n}\}
\end{equation}
as the set of equivariant maps with the constraint 
\begin{equation}
    \vchannel_i(m_{\delement}(\dtotal_i)) = \varphi(m_{\delement})(\vchannel_i(\dtotal_i))
\end{equation} 
where $\varphi:\monoid\rightarrow \monoid^{\prime}$ carries a homomorphism of monoid actions. 
\end{frame}

\begin{frame}{Example: Nominal Equivariance}
    \begin{figure}
        \includegraphics[width=1\textwidth]{figures/math/equivariance_nu.png}
        \caption{The actions on the text data are the same as the actions on the visual representation of that data as emojis.}
    \end{figure}
\end{frame}

\begin{frame}{Visualization Assembly Function}
    \begin{figure}
        \includegraphics[width=\textwidth]{figures/math/path_of_q.png}
    \end{figure}
\end{frame}

\begin{frame}{Glyph}
    The glyph is the graphic generated by $\vmark(\gbase_{\dbasepathpoint})$ where the path connected components $\dbasepath \subset \dbase$ are defined 
    \begin{equation}
    \dbasepath = \{\dbasepathpoint \in \dbase \text{ s. t. } \exists \gamma \text{ s.t. } \gamma(0)=\dbasepoint \text{ and }\gamma(1)=\dbasepathpoint\}
    \end{equation}
    such that the  path $\gamma$ from \dbasepoint\ to \dbasepathpoint\ is a continuous function from the interval [0,1] and $\gbase_{\dbasepathpoint}$ is the region
    \begin{equation}
        \begin{tikzcd}[ampersand replacement=\&]
            \gtotal \arrow[r, shift left] \& \gbase_\dbasepathpoint \arrow[rr, "\vindex(\gbasepoint)", shift left] \arrow[l, "\gsection(\gbase_\dbasepathpoint)"] \& \& \dbasepath_{\dbasepoint} \arrow[ll, "\vindex^{-1}(\dbasepath)"]
            \end{tikzcd}
        \label{eq:mark}
    \end{equation}
    such that the glyph is differentiable, in keeping with Ziemkiewicz and Kosara's description of a glyph\cite{ziemkiewiczEmbeddingInformationVisualization2009}.
\end{frame}

\begin{frame}{Visualization Equivariance}
    If \vmark\ is applied to $\vsection, \vsection^{\prime}$ that generate the same \gsection\, 
    \begin{equation}
    \vmark(\vsection) = \vmark(\vsection^{\prime})\implies \vmark(m\circ\vsection) = \vmark(m\circ\vsection^{\prime})
    \end{equation}
    then the output of both sections acted on by the same monoid $m$ must be the same. 
    \pause
    \begin{figure}[H]
        \includegraphics[width=\textwidth]{figures/math/diff_type_q.png}
    \end{figure}
\end{frame}

\begin{frame}{Scatter: $\vmark(xpos, ypos)(\alpha, \beta)$}
    \begin{figure}[H]
        \includegraphics[width=1\textwidth]{figures/math/scatter.png}
    \end{figure}

    \begin{align*}
        x &= size *\alpha \cos(\beta) + xpos \\
        y &= size *\alpha \sin(\beta) + ypos
    \end{align*}    
\end{frame}

\begin{frame}{Line: $\vmark(xpos, \hat{n_{1}}, ypos, \hat{n_{2}})(\alpha, \beta)$ }
    \begin{figure}[H]
        \includegraphics[width=1\textwidth]{figures/math/line.png}
    \end{figure}
        \begin{equation*}
            \lvert n \rvert = \sqrt{{n_{1}}^2 + {n_{2}}^2},\; 
            \hat{n_{1}} = \frac{n_1}{\lvert n \rvert}, \; \hat{n_{2}} = \frac{n_2}{\lvert n \rvert}
        \end{equation*}
    \begin{align*}
     x = xpos(\vindex(\alpha)) &+ width*\beta\hat{n_1}(\vindex(\alpha)) \\
     y = ypos(\vindex(\alpha)) &+ width*\beta\hat{n_2}(\vindex(\alpha)) 
    \end{align*}
\end{frame}

\begin{frame}{Image $\vmark(xpos, yposcolor)$}
    \begin{figure}[H]
        \includegraphics[width=1\textwidth]{figures/math/image.png}
    \end{figure}
    \begin{align*}
        R &= R(\vindex(\alpha, \beta))\\
        G &= G(\vindex(\alpha, \beta))\\
        B &= B(\vindex(\alpha, \beta))
    \end{align*}
\end{frame}

\section{References}
\begin{frame}[allowframebreaks]{References}
%\printbibliography
\end{frame}
\appendix 
\begin{frame}{Rendering: Define a Pixel}
    \begin{columns}
        \column{0.5\textwidth}
        Given a pixel
        \begin{equation}
        p=\left[y_{top}, y_{bottom}, x_{right}, x_{left}\right]
        \end{equation}
        the inverse map of the bounding box 
        \begin{equation}
        \gbase_{p} ={\gsection_{xy}}^{-1}(p)
        \end{equation}
        is a region $\gbase_p \subset \gbase$ such that 
        \begin{align}
            \scriptstyle r_p &= \scriptstyle \iint\limits_{S_p} \rho_r(s)ds^{2}\\
            \scriptstyle g_p &= \scriptstyle \iint\limits_{S_p} \rho_g(s)ds^{2}\\
            \scriptstyle  b_p &= \scriptstyle \iint\limits_{S_p} \rho_b(s)ds^{2}
        \end{align}
        yields the color of the pixel. 
        \column{0.5\textwidth}
        \begin{figure}[H]
            \includegraphics[width=\textwidth]{figures/math/render.png}
        \end{figure}
    \end{columns}
\end{frame}
